Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-21 ms.tex
tracking down one theory I have about the confusing results in subarray_size versus stability tests

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_stripe128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_stripe64.pdf}{0.33\textwidth}{SUBGRISM64}}}
{\gridline{\fig{azlab_ratio_tser_subarraySize_256.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_subarraySize_128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_subarraySize_064.pdf}{0.33\textwidth}{SUBGRISM64}}}
\caption{The subarray size tests show very similar precision levels with a background aperture horizontally displayed from the source aperture (top row).
If no background subtraction is done, paradoxically, the tallest subgrism (fewest groups) is the most stable. \textbf{\textcolor{red}{How does this make sense? Did I possibly change how the side reference pix correction was done between the 3 tests?}}}\label{fig:subarraySizes}
\end{figure*}

>>>>

\begin{figure*}
{\gridline{\fig{azlab_ratio_tser_baseline.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_stripe128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_stripe64.pdf}{0.33\textwidth}{SUBGRISM64}}}
{\gridline{\fig{azlab_ratio_tser_subarraySize_256.pdf}{0.33\textwidth}{SUBGRISM256}
\fig{azlab_ratio_tser_subarraySize_128.pdf}{0.33\textwidth}{SUBGRISM128}
\fig{azlab_ratio_tser_subarraySize_064.pdf}{0.33\textwidth}{SUBGRISM64}}}
\caption{The subarray size tests show very similar precision levels with a background aperture horizontally displayed from the source aperture (top row).
If no background subtraction is done, paradoxically, the tallest subgrism (fewest groups) is the most stable. \textbf{\textcolor{red}{How does this make sense? Did I possibly change how the side reference pix correction was done between the 3 tests? Changed from the FFT-based method to savgol on Fri Jul 12 22:04:54 2019. Processed the files on Jul 10 18:06. Could this be important? I will try and experiment on darks as well as re-processing the original baseline data to see.} }}\label{fig:subarraySizes}
\end{figure*}
